Manuscript simulations

### 2023-03-02 Manuscript simulations.Rmd
restructured repo for easier pushing

```{r}
rm(list = ls())
source("simulations/helpers.R")
source("coral.R")
```

@@

```{r}
compas_data <- readRDS("simulations/compas_data.rds")
```

>>>>

```{r}
rm(list = ls())
source("simulations_helpers.R")
source("coral.R")
```

@@

```{r}
compas_data <- readRDS("simulations_compas_data.rds")
```

```{r}
test <- one_sim(
  mat = compas_data[[1]][[1]]$Y,
  true_coords = compas_data[[1]][[1]]$true_coords,
  k = 2, 
  sim = 1, 
  niter = 100000,
  nchains = 3,
  nburnin = 50000,
  thin = 5,
  max_clus = 8,
  max_attempts = 10
)
```
